Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching

### 2018-04-13 chapter-mighes/paper.tex
geofigs

\title{Migration deconvolution}
\author{Sarah Yvonne Greer}
\maketitle

%\title{Migration deconvolution using non-stationary matching}
%\title{Approximating the inverse Hessian to enhance migration using non-stationary matching operators}
%\title{Improving migration resolution by approximating the Hessian using non-stationary matching operators}
%\title{Improving migration resolution by approximating the Hessian using non-stationary amplitude and frequency matching operators}
%\title{Improving migration resolution using non-stationary amplitude and frequency matching operators}
%\title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
%\title{Approximating the inverse Hessian to enhance migration using linear non-stationary matching operators}
%\author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
\newcommand*{\tran}{^{\mkern-1.5mu\mathsf{T}}}
\maketitle
%\inputdir{sigsbee}
\inputdir{sigsbee2}
\begin{abstract}
    We propose using two non-stationary operators to represent the amplitude and frequency variations in the least-squares Hessian to account for the principal differences between conventional and least-squares migrated images.
    The calculation and application of these operators are computationally inexpensive when compared to one iteration of least-squares migration,
    and it increases the resolution and amplitude fidelity of the migrated image.
%    When applying these transformation to a conventionally migrated image, it improves the image resolution.
    %We propose an approach of approximating the inverse Hessian operator in application to migration deconvolution. 
    %Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the Hessian---one to account for amplitude variations, and the other to account for frequency variations. 
    %Successful results were achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
    Successful results are achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
\end{abstract}

\section{Introduction}
%However, the process may be computationally expensive as it typically involves multiple iterations of forward modeling and remigrating the data. 
%Least-squares migration \cite[]{lsm} \ldots
Least-squares migration can produce an accurate migrated seismic image.
However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling and migration. 
%However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling, calculating the residual misfit, performing a conventional migration, and updating the model. 
%At the cost of approximately one iteration of least-squares migration, 
Although conventional seismic migration is less computationally expensive than least-squares migration, it generally contains migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%These artifacts are due to the fact that standard migration applies only a single adjoint operation \cite[]{pvi}.
%Least-squares migration can help alleviate 
This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by 
finding the least-squares model solution,
standard migration amounts to applying a single adjoint operation \cite[]{pvi}. 
%Conventionally migrated seismic images generally contain migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%A standard way to alleviate these artifacts 
%is an advanced way of producing an accurate image of the subsurface \cite[]{lsm}.
%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%Conventional migration is not , as such, 
%conventionally migrated images generally suffer from migration artifacts affecting amplitude fidelity and resolution. 
%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%solving the least-squares normal equations, 
%While this can be a good approximation to the inverse, and as such, is not a true inverse operation.

Various methods have attempted to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
%Migration deconvolution attempts to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image. 
Here, $\mathbf{L}$ is a standard forward-modeling operator, and $\mathbf{L}\tran$ is its adjoint---the migration operator.
These methods usually take the form of two approaches---for preconditioning before least-squares migration and as a single operation to improve accuracy of a conventionally migrated image.
%This filter approximates the inverse Hessian operator, and can be approximated by solving a data matching problem between two conventionally migrated images. 
%Migration deconvolution \cite[]{poststack,prestack}
Previously, this has been done by 
migration deconvolution \cite[]{poststack,prestack},
%stochastscally approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{diagamp}, 
approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{amp,diagamp},
and by finding and applying a bank of non-stationary matching filters \cite[]{imop,rtmmf} or deblurring filters \cite[]{debfilt} to a conventionally migrated image.
%This has traditionally been done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different operations are specified in each region \cite[]{seiinv}.
This traditionally is done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different matching filters are specified in each region \cite[]{seiinv}.

In this paper, we take a different approach. 
We note that the two primary differences between least squares migrated images and conventional migrated images are amplitude and frequency variations \cite[]{Hou2015, Hou2016}. 
%Because of this, we choose to approximate the  
Here, we treat this as a data matching problem between two conventionally migrated images, and find separate operations to account for both amplitude and frequency variations.
%However, we propose using two separate non-stationary operators---one to account for amplitude variations, and the other to account for frequency variations.

%This has advantages over previous methods as, instead of using a sliding window approach, we rely on local seismic attributes to measure and apply amplitude and frequency balancing operations \cite[]{attr}.
This approach enables us to rely on local seismic attributes to measure and apply amplitude and frequency balancing operations instead of using a sliding window approach \cite[]{attr}.
This allows for the smooth estimation and application of these matching operations instead of applying them in discrete windows.
%of local seismic attributes, and for 
%In the past, 
Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each 
%transformation 
operation
can be adjusted independently, which is another advantage of the proposed method.
To test the proposed approach, we apply this method to an example of reverse-time migration on the Sigsbee synthetic data set \cite[]{sigsbee}. 
%Least squares migration is more computationally expensive than conventional migration, but it produces a more accurate image of the subsurface---conventional migrated images generally 
%suffer from migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%exhibit less correct amplitude and frequency content. 
%applying a filter to a conventional migrated image to produce a more accurate image with less computational cost than least-squares migration. 
%Previously, this has been done using non-stationary, or spatially and temporally variant, matching filters in a sliding-window approach.

%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the migration-deconvolution image as a starting moel (red).}
%Once finding the forward operation,
\section{Theory}
The goal of least-squares migration is to find the image, $\hat{\mathbf{r}}$, that minimizes
\begin{equation}
p(\hat{\mathbf{r}}) = \frac{1}{2}\left \lVert \mathbf{\mathbf{d} - L\hat{r}} \right \rVert _2^2\;,
\end{equation}
where $\mathbf{L}$ is the forward modeling operator, representing seismic wave propagation through the subsurface, and $\mathbf{d}$ is the acquired seismic data.
This can be solved by the least-squares formulation to find $\hat{\mathbf{r}}$:
\begin{equation}
        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d}\;,
        \label{eq:ls}
\end{equation}
where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator and is typically sparse, 
%where $\mathbf{L}\tran$ is the migration operator, 
and $\left ( \mathbf{L}\tran \mathbf{L} \right )^{-1}$ is the inverse Hessian operator.
%Equation (\ref{eq:ls}) is usually solved iteratively, where each iteration costs %by multiple iteration of forward modeling
%where each iteration involves 
%On the other hand, conventional migration
Equation (\ref{eq:ls}) is usually solved iteratively, typically requiring multiple iterations of forward modeling and remigrating the seismic image \cite[]{wem,xue16}. 
Conventional migration is less computationally expensive:
\begin{equation}
        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d}.
        \label{eq:mod}
\end{equation}
%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images \cite[]{dutta14}. 
By combining equations (\ref{eq:ls}) and (\ref{eq:mod}), it is evident that
\begin{equation}
        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{0} \;,
\end{equation}
%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
so $\mathbf{m}_0$ is a distorted version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by finding a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.

%The least squares image, $\hat{\mathbf{r}}$

%Here the forward modeling operator, and subsequently the migration operator, $\mathbf{L}\tran$, depends on the type of migration; RTM vs Kirchhoff\ldots

%We can represent acquired seismic data, $\mathbf{d}$, as a forward-modeled version of the Earth's true reflectivity, 
%\begin{equation}
%        \mathbf{d} = \mathbf{L}\mathbf{r},
%\end{equation}
%where $\mathbf{r}$ is the Earth's reflectivity and $\mathbf{L}$ is the forward modeling operator CITE. 
%Least-squares migration can produce a close approximation to the Earth's reflectivity by finding the least-squares solution,
%\begin{equation}
%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d},
%        \label{eq:ls}
%\end{equation}
%but it can be computationally expensive as it typically requires multiple iterations of forward modeling and remigrating the seismic image CITE. 
%Conventional migration is less computationally expensive:
%\begin{equation}
%        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d},
%        \label{eq:mod}
%\end{equation}
%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
%However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images CITE. 
%By combining equations \ref{eq:ls} and \ref{eq:mod}, it is evident that
%\begin{equation}
%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{1},
%\end{equation}
%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
%
%In order to find $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of CITE. We begin by forward modeling the migrated image, $\mathbf{m}_9$:
%\begin{equation}
%        \mathbf{d}_2 = \mathbf{L}\mathbf{m}_0.
%\end{equation}
%We then remigrate $\mathbf{d}_2$:
%\begin{equation}
%        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_2 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0,
%\end{equation}
%and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
%\begin{equation}
%        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1.
%\end{equation}
%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.
%

\section{Method}
%Here, we follow the forward-modeling and remigration approach of

In order to approximate $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of \cite{imop}. 
We begin by forward modeling the migrated image, $\mathbf{m}_0$:
\begin{equation}
        \mathbf{d}_1 = \mathbf{L}\mathbf{m}_0 \;.
\end{equation}
We then remigrate $\mathbf{d}_1$:
\begin{equation}
        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_1 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0 \; ,
\end{equation}
and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
\begin{equation}
        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1 \;.
\end{equation}
%The inverse Hessian operator that must be applied to $\mathbf{m}_0$ to correct it closer to the least-squares migrated image, $\hat{\mathbf{r}}$, therefore, can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
%Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
This can be interpreted as a data matching problem between $\mathbf{m}_1$ and $\mathbf{m}_0$.
%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.

%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), migration migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
%\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
%Typically, the differences between least-squares migrated images and conventionally migrated images amount to only amplitude and frequency changes, 
    Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations. 
    Therefore, our approximation of $\mathbf{H}$ can be calculated from some application of a non-stationary amplitude balancing operator, $\mathbf{A}$, and a non-stationary frequency balancing operator, $\mathbf{S}$.
    %We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined. 
    We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
    We then invert our approximation to the Hessian and apply it to $\mathbf{m}_0$ to correct the amplitude and frequency content of the migrated image.

\subsection{Amplitude operator}
First, we choose to find an amplitude balancing operation that, when applied to $\mathbf{m}_0$, balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$. 
%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
This operation can be equated to a trace-by-trace multiplication of a diagonal matrix to each trace, where the matrix changes for every trace.
%The matrix $\mathbf{A}$ changes 
We estimate it by first calculating the amplitude envelope of the traces in $\mathbf{m}_0$ and $\mathbf{m}_1$, and then smoothly dividing them.
The corresponding diagonal weighting operator, $\mathbf{A}$, can be applied such that $\mathbf{m}_1 \approx \mathbf{A}\mathbf{m}_0$ to balance the amplitudes of each trace.
%to find the diagonal weighting operator 
%to balance the amplitudes of each trace.
%that balances the amplitudes of each trace of $\mathbf{m}_0$ to match with $\mathbf{m}_1$.
%This is a linear diagonal weighting operator
%This linear operator only has elements across the diagonal terms, so it is trivial to find the inverse operator. 
%Therefore, this operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
%Therefore, the operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
Since this is a linear operation that only has diagonal elements, it is trivial to find the inverse operator, $\mathbf{A}^{-1}$.

%\multiplot{2}{a0,a1}{width=1.0\columnwidth}{The forward amplitude balancing weights, $\mathbf{A}_0$ (a) and $\mathbf{A}_1$ (b).}
%\plot{rect10}{width=1.0\columnwidth}{The smoothing radius, which represents the number of samples in both spatial dimentions, that $\mathbf{m}_0$ must be smoothed over in a pyramid weight to balance local frequency content with $\mathbf{m}_1$. This represents the forward smoothing operation, $\mathbf{S}$.}

\subsection{Frequency operator}
In addition to amplitude corrections, we also attempt to account for the decrease in resolution of a conventional migrated image compared to its corresponding least-squares migrated image. 
This loss in resolution can be equated to the fact that $\mathbf{L}\tran\mathbf{L}$ acts as a blurring operator, where the conventional migrated image is a blurred version of the ideal least-squares migrated image \cite[]{poststack}. %where each individual value 
We choose to approximate this blurring using non-stationary triangle smoothing.

%This means that the 
We begin by first calculating the local frequency of the two initial images \cite[]{attr}. 
Local frequency is a temporally and spatially varying frequency attribute that smoothly varies across the image without windows.
Our goal is to find a transformation that we can apply to $\mathbf{m}_0$ that matches the local frequency content with $\mathbf{m}_1$. 
To do this, we propose using non-stationary triangle smoothing. 
%This approach involves finding and applying a non-stationary smoothing radius, which is the amount of samples, in time, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance local frequency content with $\mathbf{m}_1$. 
This approach involves finding and applying a non-stationary smoothing operator, which is the amount of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.

@@

%    Unlike $\mathbf{A}$, the smoothing operator, $\mathbf{S}$, is more challenging to invert 
%    since it is generally a banded, but not diagonal, operator and physically represents the mixing of each data point with other nearby data points.
    %This smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric. 
    %However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create false high-frequency data if inverted incorrectly without regularization.
%\multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$. This represents the forward smoothing operation, $\mathbf{S}$.}

>>>>

\title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
\author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
\newcommand*{\tran}{^{\mkern-1.5mu\mathsf{T}}}
\maketitle
\inputdir{sigsbee}
\begin{abstract}
    We propose using two non-stationary operators to represent the amplitude and frequency variations in the least-squares Hessian to account for the principal differences between conventional and least-squares migrated images.
    The calculation and application of these operators are computationally inexpensive when compared to one iteration of least-squares migration, and it increases the resolution and amplitude fidelity of the migrated image.
    Successful results are achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
\end{abstract}

\section{Introduction}
    Least-squares migration can produce an accurate migrated seismic image.
    However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling and migration. 
    Although conventional seismic migration is less computationally expensive than least-squares migration, it generally contains migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
    This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by finding the least-squares model solution, standard migration amounts to applying a single adjoint operation \cite[]{pvi}.

    Various methods have attempted to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
    Here, $\mathbf{L}$ is a standard forward-modeling operator, and $\mathbf{L}\tran$ is its adjoint---the migration operator.
    These methods usually take the form of two approaches---for preconditioning before least-squares migration and as a single operation to improve accuracy of a conventionally migrated image.
    Previously, this has been done by migration deconvolution \cite[]{poststack,prestack}, approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{amp,diagamp}, and by finding and applying a bank of non-stationary matching filters \cite[]{imop,rtmmf} or deblurring filters \cite[]{debfilt} to a conventionally migrated image.
    This traditionally is done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different matching filters are specified in each region \cite[]{seiinv}.

    In this paper, we take a different approach. 
    We note that the two primary differences between least squares migrated images and conventional migrated images are amplitude and frequency variations \cite[]{Hou2015, Hou2016}. 
    Here, we treat this as a data matching problem between two conventionally migrated images, and find separate operations to account for both amplitude and frequency variations.

    This approach enables us to rely on local seismic attributes to measure and apply amplitude and frequency balancing operations instead of using a sliding window approach \cite[]{attr}.
This allows for the smooth estimation and application of these matching operations instead of applying them in discrete windows.
    Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each operation can be adjusted independently, which is another advantage of the proposed method.
    To test the proposed approach, we apply this method to an example of reverse-time migration on the Sigsbee synthetic data set \cite[]{sigsbee}.

\section{Theory}
    The goal of least-squares migration is to find the image, $\hat{\mathbf{r}}$, that minimizes
    \begin{equation}
        p(\hat{\mathbf{r}}) = \frac{1}{2}\left \Vert \mathbf{\mathbf{d} - L\hat{r}} \right \Vert _2^2\;,
        %p(\hat{\mathbf{r}}) = \frac{1}{2}\left \lVert \mathbf{\mathbf{d} - L\hat{r}} \right \rVert _2^2\;,
    \end{equation}
    where $\mathbf{L}$ is the forward modeling operator, representing seismic wave propagation through the subsurface, and $\mathbf{d}$ is the acquired seismic data.
    This can be solved by the least-squares formulation to find $\hat{\mathbf{r}}$:
    \begin{equation}
        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d}\;,
        \label{eq:ls}
    \end{equation}
    where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator and is typically sparse, and $\left ( \mathbf{L}\tran \mathbf{L} \right )^{-1}$ is the inverse Hessian operator.
    Equation (\ref{eq:ls}) is usually solved iteratively, typically requiring multiple iterations of forward modeling and remigrating the seismic image \cite[]{wem,xue16}. 
Conventional migration is less computationally expensive:
\begin{equation}
    \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d}.
    \label{eq:mod}
\end{equation}
    However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images \cite[]{dutta14}. 
    By combining equations (\ref{eq:ls}) and (\ref{eq:mod}), it is evident that
\begin{equation}
    \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{0} \;,
\end{equation}
    so $\mathbf{m}_0$ is a distorted version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by finding a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.

\section{Method}
    In order to approximate $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of \cite{imop}. 
    We begin by forward modeling the migrated image, $\mathbf{m}_0$:
    \begin{equation}
        \mathbf{d}_1 = \mathbf{L}\mathbf{m}_0 \;.
    \end{equation}
    We then remigrate $\mathbf{d}_1$:
    \begin{equation}
        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_1 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0 \; ,
    \end{equation}
    and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
    \begin{equation}
        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1 \;.
    \end{equation}
    Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
    This can be interpreted as a data matching problem between $\mathbf{m}_1$ and $\mathbf{m}_0$.

\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
    Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations. 
    Therefore, our approximation of $\mathbf{H}$ can be calculated from some application of a non-stationary amplitude balancing operator, $\mathbf{A}$, and a non-stationary frequency balancing operator, $\mathbf{S}$.
    We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
    We then invert our approximation to the Hessian and apply it to $\mathbf{m}_0$ to correct the amplitude and frequency content of the migrated image.

\subsection{Amplitude operator}
    First, we choose to find an amplitude balancing operation that, when applied to $\mathbf{m}_0$, balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$. 
    This operation can be equated to a trace-by-trace multiplication of a diagonal matrix to each trace, where the matrix changes for every trace.
    We estimate it by first calculating the amplitude envelope of the traces in $\mathbf{m}_0$ and $\mathbf{m}_1$, and then smoothly dividing them.
    The corresponding diagonal weighting operator, $\mathbf{A}$, can be applied such that $\mathbf{m}_1 \approx \mathbf{A}\mathbf{m}_0$ to balance the amplitudes of each trace.
    Since this is a linear operation that only has diagonal elements, it is trivial to find the inverse operator, $\mathbf{A}^{-1}$.

\subsection{Frequency operator}
    In addition to amplitude corrections, we also attempt to account for the decrease in resolution of a conventional migrated image compared to its corresponding least-squares migrated image. 
    This loss in resolution can be equated to the fact that $\mathbf{L}\tran\mathbf{L}$ acts as a blurring operator, where the conventional migrated image is a blurred version of the ideal least-squares migrated image \cite[]{poststack}. 
    We choose to approximate this blurring using non-stationary triangle smoothing.

    We begin by first calculating the local frequency of the two initial images \cite[]{attr}. 
    Local frequency is a temporally and spatially varying frequency attribute that smoothly varies across the image without windows.
    Our goal is to find a transformation that we can apply to $\mathbf{m}_0$ that matches the local frequency content with $\mathbf{m}_1$. 
    To do this, we propose using non-stationary triangle smoothing. 
    This approach involves finding and applying a non-stationary smoothing operator, which is the amount of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.

@@

    \multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$. This represents the forward smoothing operation, $\mathbf{S}$.}

\subsection{Calculating the inverse Hessian}
    Now that we have found the forward operators that separately balance amplitude and frequency content from $\mathbf{m}_0$ to $\mathbf{m_1}$, where $\mathbf{m}_1 \approx \mathbf{H} \mathbf{m}_0$, we want to find what combination of $\mathbf{A}$ and $\mathbf{S}$ best approximates $\mathbf{H}$.
    Since $\mathbf{H} = \mathbf{L}\tran\mathbf{L}$ is symmetric, we want our approximation of $\mathbf{H}$ to be as close to symmetric as possible.
    Therefore, we define $\mathbf{H}$ as
    \begin{equation}
        \mathbf{H} \approx \mathbf{A}^{\sfrac{1}{2}}\mathbf{S}\mathbf{A}^{\sfrac{1}{2}} \;,
    \end{equation}
    where $\mathbf{A}$ is the operator that balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, and $\mathbf{S}$ is the operator that balances the local frequency content of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, both defined previously.
    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be symmetric, since both $\mathbf{A}$ and $\mathbf{S}$ are symmetric operations. 
    Splitting up our approximation to the Hessian into two separate operators allows us to control how much of each operation and the order of each operation goes into correcting the image, and see how it affects the resulting image.
    Now that we have found the forward Hessian, $\mathbf{H}$, such that $\mathbf{H}\mathbf{m}_0 \approx \mathbf{m}_1$ using data matching operators, we want to find the inverse of this operator, $\mathbf{H}^{-1}$, such that $\hat{\mathbf{r}} \approx \mathbf{H} ^{-1} \mathbf{m}_0$ provides us with the least-squares image.
    This is found as
    \begin{equation}
        \mathbf{H}^{-1} \approx \left ( \mathbf{A}^{\sfrac{1}{2}} \mathbf{S} \mathbf{A}^{\sfrac{1}{2}} \right )^{-1} = 
        \mathbf{A}^{\sfrac{-1}{2}} \mathbf{S}^{-1} \mathbf{A}^{\sfrac{-1}{2}}\;.
        \label{eq:invh}
    \end{equation}

    Since the amplitude operators only contain diagonal terms, they are simple to invert. 
    However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create physically unrealistic high-frequency data if inverted incorrectly without regularization.
    Therefore, $\mathbf{S}^{-1}$ must be calculated with care to ensure the inverted data is physically plausible. 
    We iteratively invert $\mathbf{S}$ using shaping regularization \cite[]{shap}, where the shaping operator is a bandpass filter picked to ensure the passband contains only physically possible frequencies for the given data set.
    The cost of applying our approximation to $\mathbf{H}^{-1}$ in equation (\ref{eq:invh}) is $\mathcal{O}(N)$, where $N$ is the image size. 
    The constant is small, typically around 10 for the number of iterations, and the calculation and application of this approximation is computationally insignificant compared to one iteration of least-squares migration.

    \plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}
